BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-13 tex/4-techniques.tex
Add Click click scripting paragraph under techniques.

% The solution
To support blogs with JavaScript generated content we embed a full web browser into the crawler. After considering mutliple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performences and scipting capabilities. In order to take full advantage of all extraction capabilities, the JavaScript rendering is done as the very first step of blog post processing. This way, every other part of the project is independent of whether or not the page its currently processing was actually rendered by PhantomJS or comes directly from the web server. Extracting blog post content, comments and images therefore works equally well on both blogs with JavaScript generated content and traditional HTML blogs.

- python scripting click click use case

\subsection{Architecture}
\subsubsection{Item pipeline}
- item pipeline, modularity \\

\subsubsection{Scalability}
- http://www.reactivemanifesto.org/
- stateless \\
- scrapyd \\

@@

>>>>

% The solution
To support blogs with JavaScript generated content we embed a full web browser into the crawler. After considering mutliple option, we opted for PhantomJS\cite{phantomjs2013}, a headless web browser with great performences and scipting capabilities. In order to take full advantage of all the extraction functionalities, the JavaScript rendering is done as the very first step of blog post processing. This way, every other part of the project is independent of whether or not the page its currently processing was actually rendered by PhantomJS or comes directly from the web server. Extracting blog post content, comments and images therefore works equally well on both blogs with JavaScript generated content and traditional HTML blogs.

% Click click scripting
In addition to extracting page after JavaScript execution, we also use some of PhantomJS scripting capabilities. When the number of comments on one page exceeds a certain threshold, both Disqus and LiveFyre only load a subset of them and end the stream of comments with a "Show More Comments" buttons. As part of the page load process we instruct PhantomJS to repeatedly click on this button until all comments are loaded. As you will see in the evaluation section, \TODO{we will see..}

% \subsection{Architecture}
% \subsubsection{Item pipeline}
% - item pipeline, modularity \\

@@

\subsubsection{Scalability}
At the time of writing...
- http://www.reactivemanifesto.org/
- stateless \\
- scrapyd \\
